### 2016-08-26 section/1_under.tex
in the middle of moving threats to validity

\noindent\textbf{Threats to Validity}
Intuitively, the categories above cover a lot of common inefficient
loop problems; each sub-category is concrete enough to guide the design of a
failure diagnosis tool; none of the categories above involve any application
specific knowledges or heuristics.
Of course, our taxonomy does not cover \emph{all} loop inefficiency problems.
For example, some loops may be vulnerable to false sharing problems or lock
contention problems, which are out of the scope of our taxonomy.

>>>>

Intuitively, the above categories above cover many common inefficient
loop problems; each sub-category is concrete enough to guide the design of a
diagnosis tool; none of these (sub-)categories involve application
specific knowledges or heuristics.

### 2016-08-26 section/2_workless.tex
in the middle of moving threats to validity

\Tool considers two types of instructions as side-effect instructions:
(1) write to heap or global variables;
(2) write to a stack variable, defined outside the loop, and the update value
may be used after the loop. The second condition is checked through liveness
analysis.
\Tool also analyzes all functions called
by a loop directly or indirectly --- a function $F$ that updates variables
defined outside $F$ makes the corresponding call statement in $F$'s
caller a side-effect instruction.
\comment{
We consider all calls to library functions or through function pointers 
as having side effects, 
unless the library functions are specially marked by us in a white list.
}
This analysis is complete, but not sound. We may identify side-effect
instructions that are actually not. %to be moved to threats to validity

>>>>

\Tool considers two types of instructions as side-effect instructions:
(1) writes to heap or global variables;
(2) writes to a stack variable defined outside the loop and
may be used after the loop.
The second condition is checked through liveness analysis.
\Tool also analyzes all functions called
by a loop directly or indirectly --- a function $F$ that updates variables
defined outside $F$ makes the corresponding call statement in $F$'s
caller a side-effect instruction.
\comment{
We consider all calls to library functions or through function pointers 
as having side effects, 
unless the library functions are specially marked by us in a white list.
}
 %to be moved to threats to validity
